\section{Mobile Techniques}
\label{sec:mobile}

\subsection{Vision Sensors}
\label{subsec:vision}
% 这一部分主要讨论如何使用视觉传感器，可以怎样使用视觉传感器，研究项目中都怎样使用了视觉传感器来进行情感计算
This part mainly discusses vision sensors, which includes RGB camera and depth camera.
illustrate how vision sensor can be used for affective computing, mainly cite these papers: ...

Vision sensors are important because of they can directly tells user's face emotion, which is
the direct emotional communication method between humans.

\subsection{Touch Sensors}
\label{subsec:touch}
\cite{Gao2012, Shah2015, Hertenstein2009, bhattacharya2017predictive}
% 这一部分主要讨论如何使用触摸传感器，可以触摸传感器的不同类型，研究项目中都是怎样使用触摸传感器的特征的？
% 几个可能的方面
% 1. 有文章显示 touch 行为可以进行情感交流 \cite{Hertenstein2009}
% 2. 在特定的应用情境下，有文章显示 touxh 行为可以推导当前的用户情感..cite???  这篇文章则提出了
% 3. 有文章首先总结了 haptic-based affect detection remains an understudy topic; \cite{Bhattacharya2017}
% 4. 既然触摸行为在表达情感上具有重要的指示，那么反过来如何用通过触摸来表达情感\cite{Lentini2017}\cite{Mazzoni2016}
This part mainly discusses touch sensors, which includes capacitive touch screen and 3D touch screen.
And also explain why touch sensor can be used for affective computing (they are applicable
because of specific application context), mainly cite these papers: ...

\subsection{Motion Sensors}
\label{subsec:motion}
This part illustrate \cite{Rana, Mottelson2016, Bailenson2007}

Motion sensors become important because it could tells us what is user's body language.

\subsection{Audio Sensors}
\label{subsec:audio}

Audio sensors mainly infers to input and output microphones. This leans two part of affective computing:

First is inferring emotions from user speech. 
This task can also split as two part of inferring task, and one is directly infer from voice;
another is recognize speech text from user, then understanding or inferring from text.

Second is output a emotional speech from machines.

\subsection{GPS Sensors}
\label{subsec:gps}

\subsection{Application Context}
\label{subsec:ui}

\subsection{Techniques Fusion}
\label{subsec:fusion}

% 写作思路：
% 我们首先发现了一篇全面介绍关于技术融合的文章，我们从这篇文章中抽取出移动平台能够使用的部分 \cite{Mazzoni2016}

This section should present a table for the combination of previous sensors.
